---
title: "ED Quantitative Analysis"
author: "Danny Sack"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    code_folding: hide
    lightbox: true
    code_download: true
---

```{r setup, include=FALSE}
# load packages
library(tidyverse)
library(ggpubr)
library(extrafont)
library(Hmisc)
library(gtsummary)
library(ggdist)
library(gghalves)
library(sdamr)
library(rnoaa)
library(scales)
loadfonts()
knitrSet(lang='markdown', fig.path='png/', fig.align='center', w=9, h=8, cache=TRUE)
options(knitr.kable.NA = '')
options(noaakey = "dGFZnaNPcYqMsRIhDhEMxzSCgvmWmZqr")
```

```{r import_data}
# start by setting a seed
Load(data)

# create theme for plots
theme1 <- theme_pubr() +
  theme(text = element_text(family = "Arial"),
        axis.text.x = element_text(angle = 90),
        legend.position = "bottom")
```

# Table 1

```{r gen_tab1}
tbl_summary(data %>% mutate(vis_num = as.numeric(vis_num),
                            vis_hour = as.numeric(vis_hour),
                            time_to_room = as.numeric(time_to_room)/60, # to make it minutes
                            time_to_md = as.numeric(time_to_md)/60, # to make it minutes
                            priorEdVisits = as.numeric(priorEdVisits),
                            priorAdmits = as.numeric(priorAdmits),
                            avg_prior_hosp_los = as.numeric(avg_prior_hosp_los)) %>%
              select(age_yr, age_cat, sex, lang_cat, race, eth_cat, insurance_cat,
                     meansOfArrival, hospDispoCat, edDispoCat, cc_cat, ed_dx_cat,
                     pastQuestion:screenedQuestion, psychHist, 
                     acuity_level_c, vis_num, vis_month:time_to_ed_dc, priorEdVisits:avg_prior_hosp_los),
            by = housing_cat)
```

## Table 1 at participants' first visit


```{r gen_tab1_ind}
print("Table 1, but only including the first registered visit in the study period")
tbl_summary(data %>% mutate(vis_num = as.numeric(vis_num),
                            vis_hour = as.numeric(vis_hour),
                            time_to_room = as.numeric(time_to_room)/60, # to make it minutes
                            time_to_md = as.numeric(time_to_md)/60, # to make it minutes
                            priorEdVisits = as.numeric(priorEdVisits),
                            priorAdmits = as.numeric(priorAdmits),
                            avg_prior_hosp_los = as.numeric(avg_prior_hosp_los)) %>%
              select(age_yr, age_cat, sex, lang_cat, race, eth_cat, insurance_cat,
                     meansOfArrival, hospDispoCat, edDispoCat, cc_cat, ed_dx_cat,
                     pastQuestion:screenedQuestion, psychHist, 
                     acuity_level_c, vis_num, vis_month:time_to_ed_dc, priorEdVisits:avg_prior_hosp_los) %>%
              filter(vis_num == 1),
            by = housing_cat)
```

# Visits During the Study Period

```{r ed_visits}
ggplot(data, aes(x = as.numeric(vis_num), y = housing_cat)) +
  stat_halfeye(trim = TRUE) +
  geom_point(size = 0.5, alpha = 0.25, position = position_jitternudge(jitter.width = 0.1, jitter.height = 0.35, nudge.x = -0.05)) +
  ggtitle("ED Visits from Jan 1-May 16, 2023") +
  ylab("Housing Status") +
  xlab("Visits") +
  theme1
```

# Time to Room

```{r room_time}
ggplot(data, aes(x = as.numeric(time_to_room)/60, y = housing_cat)) +
  stat_halfeye(trim = TRUE) +
  geom_point(size = 0.5, alpha = 0.25, position = position_jitternudge(jitter.width = 0.1, jitter.height = 0.35, nudge.x = -0.1)) +
  coord_cartesian(xlim = c(0, 20)) +
  ggtitle("Minutes to room") +
  ylab("Housing Status") +
  xlab("Minutes") +
  theme1
```

# Time to Provider

```{r md_time}
ggplot(data, aes(x = as.numeric(time_to_md)/60, y = housing_cat)) +
  stat_halfeye(trim = TRUE) +
  geom_point(size = 0.5, alpha = 0.25, position = position_jitternudge(jitter.width = 0.1, jitter.height = 0.35, nudge.x = -0.1)) +
  coord_cartesian(xlim = c(0, 480)) +
  ggtitle("Time Until Provider Assigned") +
  ylab("Housing Status") +
  xlab("Minutes") +
  theme1

# wilcoxin p-values

# housing v. unstable 
wilcox.test(data %>% filter(housing_cat == "Stable Housing") %>% pull(time_to_md),
            data %>% filter(housing_cat == "Unstable Housing") %>% pull(time_to_md))

# housing v. houseless
wilcox.test(data %>% filter(housing_cat == "Stable Housing") %>% pull(time_to_md),
            data %>% filter(housing_cat == "Homeless") %>% pull(time_to_md))

# unstable v. houseless
wilcox.test(data %>% filter(housing_cat == "Unstable Housing") %>% pull(time_to_md),
            data %>% filter(housing_cat == "Homeless") %>% pull(time_to_md))
```

# Time to ED Dispo

```{r ed_dispo_time}
ggplot(data, aes(x = as.numeric(time_to_ed_dc)/60, y = housing_cat)) +
  stat_halfeye(trim = TRUE) +
  geom_point(size = 0.5, alpha = 0.25, position = position_jitternudge(jitter.width = 0.1, jitter.height = 0.35, nudge.x = -0.1)) +
  coord_cartesian(xlim = c(0, 100)) +
  ggtitle("Time Until ED Disposition Plan") +
  ylab("Housing Status") +
  xlab("Minutes") +
  theme1

# wilcoxin p-values

# housing v. unstable 
wilcox.test(data %>% filter(housing_cat == "Stable Housing") %>% pull(time_to_ed_dc),
            data %>% filter(housing_cat == "Unstable Housing") %>% pull(time_to_ed_dc))

# housing v. houseless
wilcox.test(data %>% filter(housing_cat == "Stable Housing") %>% pull(time_to_ed_dc),
            data %>% filter(housing_cat == "Homeless") %>% pull(time_to_ed_dc))

# unstable v. houseless
wilcox.test(data %>% filter(housing_cat == "Unstable Housing") %>% pull(time_to_ed_dc),
            data %>% filter(housing_cat == "Homeless") %>% pull(time_to_ed_dc))
```

# Time to Hosp d/c

```{r hospdc_time}
ggplot(data, aes(x = as.numeric(time_to_hosp_dc)/60, y = housing_cat)) +
  stat_halfeye(trim = TRUE) +
  geom_point(size = 0.5, alpha = 0.25, position = position_jitternudge(jitter.width = 0.1, jitter.height = 0.35, nudge.x = -0.1)) +
  coord_cartesian(xlim = c(0, 480)) +
  ggtitle("Time Until Discharge") +
  ylab("Housing Status") +
  xlab("Minutes") +
  theme1
```

# Triage Score

```{r triage}
ggplot(data, aes(x = acuity_level_c, y = housing_cat)) +
  stat_halfeye(trim = TRUE) +
  geom_point(size = 0.5, alpha = 0.25, position = position_jitternudge(jitter.width = 0.1, jitter.height = 0.35, nudge.x = -0.05)) +
  ggtitle("Triage Score") +
  ylab("Housing Status") +
  xlab("Score") +
  theme1
```

# Age

```{r age}
ggplot(data, aes(x = age_yr, y = housing_cat)) +
  stat_halfeye(trim = TRUE) +
  geom_point(size = 0.5, alpha = 0.25, position = position_jitternudge(jitter.width = 0.1, jitter.height = 0.35, nudge.x = -0.05)) +
  ggtitle("Age") +
  ylab("Housing Status") +
  xlab("Year") +
  theme1
```

# Covariates by Month Graphs (all)

## Age

```{r age_cat}
age_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = age_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("A) Age") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 2)) +
  theme1

## WITH PERCENTAGES
# data %>%
#   select(housing_cat, vis_month, age_cat) %>%
#   group_by(housing_cat, vis_month, age_cat) %>%
#   summarise(n = n()) %>%
#   group_by(housing_cat, vis_month) %>%
#   mutate(tot = sum(n)) %>%
#   ungroup() %>%
#   mutate(prop = n/tot) %>%
#   ggplot(aes(x = vis_month, y = prop, fill = age_cat)) +
#   geom_col() +
#   geom_text(aes(label = percent(accuracy = 1, ifelse(prop > 0.0499, prop, NA))),
#             position = position_fill(vjust = 0.5),
#             size = 2.25) +
#   facet_grid(rows = ~housing_cat) +
#   ggtitle("A) Age") +
#   xlab("") +
#   scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
#   scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
#   guides(fill = guide_legend(nrow = 2)) +
#   theme1
```

## Sex

```{r sex_graph}
sex_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = sex), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("B) Sex") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 2)) +
  theme1
```


## Language

```{r lang_graph}
lang_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = lang_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("C) Language") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 2)) +
  theme1
```

## Race

```{r race_graph}
race_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = race), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("D) Race") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 5)) +
  theme1
```

## Ethnicity

```{r ethnicity_graph}
eth_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = eth_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("E) Ethnicity") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 5)) +
  theme1
```

## Insurance
```{r insurance_graph}
ins_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = insurance_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("F) Insurance") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 5)) +
  theme1
```

### Figure 1 - Demographics

```{r fig1_demo, fig.height=15, fig.width=18}
# quartz(type = "pdf", file = "pdfs/insurance.pdf", height = 8, w = 10)
ggarrange(age_fig, sex_fig, lang_fig, race_fig, eth_fig, ins_fig)
# dev.off()
# # embed the font
# embed_fonts("pdfs/insurance.pdf")
```

## Arrival Method

```{r arrival_graph}
ar_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = meansOfArrival), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("A) Arrival Method") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```

## ED Disposition

```{r eddispo_graph}
eddc_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = edDispoCat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("B) ED Disposition") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```

## Hospital Discharge

```{r hospdc_graph}
hospdc_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = hospDispoCat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("C) Hospital Discharge Location") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```

## Acuity Level

```{r acuity_graph}
triage_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = factor(acuity_level_c)), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("D) Intake Triage Scores") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```

## Chief Complaint

```{r cc_graph}
cc_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = cc_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("E) Chief Complaint Category") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```

## ED Primary Diagnosis

```{r pdx_graph}
eddx_fig <- ggplot(data, aes(x = vis_month)) +
  geom_bar(aes(fill = ed_dx_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("F) Primary ED Discharge Diagnosis") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```


### Figure 2 - Clinical

```{r fig2_clin, fig.height=15, fig.width=18}
# quartz(type = "pdf", file = "pdfs/insurance.pdf", height = 8, w = 10)
ggarrange(ar_fig, eddc_fig, hospdc_fig, triage_fig, cc_fig, eddx_fig)
# dev.off()
# # embed the font
# embed_fonts("pdfs/insurance.pdf")
```

# Covariates by Month (high utilizers)

```{r high_ut_data}
hu_data <- data %>% 
  group_by(id) %>%
  mutate(tot_vis = max(vis_num),
         tot_vis_fac = factor(ifelse(tot_vis > 4, "5+", tot_vis), levels = c("1", "2", "3", "4", "5+"))) %>%
  ungroup() %>%
  filter(tot_vis > 2)
```

## Table 2

```{r gen_tab2}
tbl_summary(hu_data %>% mutate(vis_num = as.numeric(vis_num),
                            vis_hour = as.numeric(vis_hour),
                            time_to_room = as.numeric(time_to_room)/60, # to make it minutes
                            time_to_md = as.numeric(time_to_md)/60, # to make it minutes
                            priorEdVisits = as.numeric(priorEdVisits),
                            priorAdmits = as.numeric(priorAdmits),
                            avg_prior_hosp_los = as.numeric(avg_prior_hosp_los)) %>%
              select(age_yr, age_cat, sex, lang_cat, race, eth_cat, insurance_cat,
                     meansOfArrival, hospDispoCat, edDispoCat, cc_cat, ed_dx_cat,
                     pastQuestion:screenedQuestion, psychHist, 
                     acuity_level_c, vis_num, vis_month:time_to_ed_dc, priorEdVisits:avg_prior_hosp_los),
            by = housing_cat)
```

## Visits per patient

```{r vis_per_pt}
print("total visits by visits")
data %>% select(id, vis_num, housing_screen) %>%
  group_by(id) %>%
  mutate(tot_vis = max(vis_num),
         tot_vis_fac = factor(ifelse(tot_vis > 4, "5+", tot_vis), levels = c("1", "2", "3", "4", "5+"))) %>%
  ungroup() %>%
  select(housing_screen, tot_vis_fac) %>%
  tbl_summary(by = housing_screen)

print("total visits by people")
data %>% select(id, vis_num, housing_screen) %>%
  group_by(id) %>%
  mutate(tot_vis = max(vis_num),
         tot_vis_fac = factor(ifelse(tot_vis > 4, "5+", tot_vis), levels = c("1", "2", "3", "4", "5+"))) %>%
  ungroup() %>%
  distinct(., id, .keep_all = TRUE) %>%
  select(housing_screen, tot_vis_fac) %>%
  tbl_summary(by = housing_screen)

# graph of total visits per person
high_patients <- data %>% 
  group_by(id) %>%
  mutate(Encounters = max(vis_num),
        Visits = factor(ifelse(Encounters > 4, "5+", Encounters), levels = c("1", "2", "3", "4", "5+"))) %>%
  ungroup() %>%
  select(id, housing_screen, Encounters, Visits) %>%
  distinct(., id, .keep_all = TRUE)

high_encounters <- data %>% 
  group_by(id) %>%
  mutate(Encounters = max(vis_num),
        Visits = factor(ifelse(Encounters > 4, "5+", Encounters), levels = c("1", "2", "3", "4", "5+"))) %>%
  ungroup() %>%
  select(id, housing_screen, Encounters, Visits)

# graph of patients by housing screen
tot_pts_use <- high_patients %>% 
  select(housing_screen, Visits) %>%
  filter(housing_screen != "Missing") %>%
  group_by(housing_screen, Visits) %>%
  summarise(visits = n()) %>%
  group_by(housing_screen) %>%
  mutate(tot = sum(visits)) %>%
  ungroup() %>%
  mutate(prop = visits/tot) %>%
  ggplot(aes(x = housing_screen, y = prop, fill = Visits)) +
  geom_col() +
  geom_text(aes(label = percent(accuracy = 0.1, ifelse(prop > 0.0499, prop, NA))),
            position = position_fill(vjust = 0.5)) +
  labs(title = "A) All VUMC ED Patients", subtitle = "") +
  xlab("Experiencing Homelessness") +
  scale_y_continuous(name = "Percentage", labels = label_percent()) +
  scale_fill_brewer(type = "qual", palette = "Paired") +
  guides(fill = guide_legend(nrow = 2)) +
  theme1

tot_encounters_use <- high_encounters %>% 
  select(housing_screen, Visits) %>%
  filter(housing_screen != "Missing") %>%
  group_by(housing_screen, Visits) %>%
  summarise(visits = n()) %>%
  group_by(housing_screen) %>%
  mutate(tot = sum(visits)) %>%
  ungroup() %>%
  mutate(prop = visits/tot) %>%
  ggplot(aes(x = housing_screen, y = prop, fill = Visits)) +
  geom_col() +
  geom_text(aes(label = percent(accuracy = 0.1, ifelse(prop > 0.0499, prop, NA))),
            position = position_fill(vjust = 0.5)) +
  labs(title = "B) All VUMC ED Encounters", subtitle = "") +
  xlab("Experiencing Homelessness") +
  scale_y_continuous(name = "", labels = label_percent()) +
  scale_fill_brewer(type = "qual", palette = "Paired") +
  guides(fill = guide_legend(nrow = 2)) +
  theme1
```

## Repeat ED Visits

```{r repeat_visits}
# create timeline for time between visits
repeat_vis <- data %>% 
  group_by(id) %>%
  mutate(tot_vis = max(vis_num),
         tot_vis_fac = factor(ifelse(tot_vis > 4, "5+", tot_vis), levels = c("1", "2", "3", "4", "5+"))) %>%
  ungroup() %>%
  select(id, housing_screen, vis_num, tot_vis, 
         tot_vis_fac, vis_date) %>%
  filter(tot_vis > 1) %>% 
  group_by(id) %>%
  mutate(last_vis_date = lag(vis_date)) %>%
  ungroup() %>%
  mutate(days_bt_vis = difftime(vis_date, last_vis_date, units = "days"),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) > 30, "30+ days", NA),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) < 31, "30  or fewer days", bt_vis_cat),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) < 15, "14  or fewer days", bt_vis_cat),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) < 8, "7  or fewer days", bt_vis_cat),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) < 6, "5  or fewer days", bt_vis_cat),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) < 4, "3 or fewer days", bt_vis_cat),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) < 1, "<1 day", bt_vis_cat),
         bt_vis_cat = factor(bt_vis_cat, levels = c("<1 day", "3  or fewer days", 
                                                    "5  or fewer days", "7  or fewer days", 
                                                    "14  or fewer days", "30  or fewer days", 
                                                    "30+ days")))

# plot it
ggplot(repeat_vis, aes(x = as.numeric(days_bt_vis), y = housing_screen)) +
  stat_halfeye(trim = TRUE) +
  geom_point(size = 0.5, alpha = 0.25, position = position_jitternudge(jitter.width = 0.1, jitter.height = 0.35, nudge.x = -0.05)) +
  ggtitle("Time Between Consecutive Visits") +
  ylab("Experiencing Homelessness") +
  xlab("Days") +
  theme1

# only includes second visit and beyond
repvis_fig <- repeat_vis %>% 
  filter(!is.na(bt_vis_cat)) %>%
  select(housing_screen, bt_vis_cat) %>%
  filter(housing_screen != "Missing") %>%
  group_by(housing_screen, bt_vis_cat) %>%
  summarise(people = n()) %>%
  group_by(housing_screen) %>%
  mutate(tot = sum(people)) %>%
  ungroup() %>%
  mutate(prop = people/tot) %>%
  ggplot(aes(x = housing_screen, y = prop, fill = fct_rev(bt_vis_cat))) +
  geom_col() +
  geom_text(aes(label = percent(accuracy = 0.1, ifelse(prop > 0.0499, prop, NA))),
            position = position_fill(vjust = 0.5)) +
  labs(title = "C) Next ED Visit", subtitle = "Among participants with 1+ ED visits") +
  xlab("Experiencing Homelessness") +
  scale_y_continuous(name = "", labels = label_percent()) +
  scale_fill_brewer(name = "Time", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 2)) +
  theme1
```
## Repeat ED Visits After Admission - TBD

```{r rep_visits_admission}
# create timeline for time between visits
post_admit_vis <- data %>% 
  group_by(id) %>%
  mutate(tot_vis = max(vis_num),
         tot_vis_fac = factor(ifelse(tot_vis > 4, "5+", tot_vis), levels = c("1", "2", "3", "4", "5+"))) %>%
  ungroup() %>%
  select(id, housing_screen, edDispoCat, vis_num, tot_vis, 
         tot_vis_fac, vis_date) %>%
  filter(tot_vis > 1) %>% 
  group_by(id) %>%
  mutate(last_vis_date = lag(vis_date),
         last_dispo = lag(edDispoCat)) %>%
  ungroup() %>%
  filter(last_dispo == "Admit") %>%
  mutate(days_bt_vis = difftime(vis_date, last_vis_date, units = "days"),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) > 30, "30+ days", NA),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) < 31, "30  or fewer days", bt_vis_cat),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) < 15, "14  or fewer days", bt_vis_cat),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) < 8, "7  or fewer days", bt_vis_cat),
         bt_vis_cat = ifelse(as.numeric(days_bt_vis) < 1, "<1 day", bt_vis_cat),
         bt_vis_cat = factor(bt_vis_cat, levels = c("<1 day", "7  or fewer days", 
                                                    "14  or fewer days", "30  or fewer days", 
                                                    "30+ days")))

# plot it
ggplot(post_admit_vis, aes(x = as.numeric(days_bt_vis), y = housing_screen)) +
  stat_halfeye(trim = TRUE) +
  geom_point(size = 0.5, alpha = 0.25, position = position_jitternudge(jitter.width = 0.1, jitter.height = 0.35, nudge.x = -0.05)) +
  ggtitle("Time Between Admission and Next ED Visit") +
  ylab("Experiencing Homelessness") +
  xlab("Days") +
  theme1

# only includes second visit and beyond
repvisadm_fig <- post_admit_vis %>% 
  filter(!is.na(bt_vis_cat)) %>%
  select(housing_screen, bt_vis_cat) %>%
  filter(housing_screen != "Missing") %>%
  group_by(housing_screen, bt_vis_cat) %>%
  summarise(people = n()) %>%
  group_by(housing_screen) %>%
  mutate(tot = sum(people)) %>%
  ungroup() %>%
  mutate(prop = people/tot) %>%
  ggplot(aes(x = housing_screen, y = prop, fill = fct_rev(bt_vis_cat))) +
  geom_col() +
  geom_text(aes(label = percent(accuracy = 0.1, ifelse(prop > 0.0499, prop, NA))),
            position = position_fill(vjust = 0.5)) +
  labs(title = "D) Next ED Visit After Admission", subtitle = "Among participants with 1+ ED visits") +
  xlab("Experiencing Homelessness") +
  scale_y_continuous(name = "", labels = label_percent()) +
  scale_fill_brewer(name = "Time", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 2)) +
  theme1
```

## Figure 3 - ED Utilization Characteristics

```{r fig3, fig.height=10, fig.width=8}
top <- ggarrange(tot_pts_use, tot_encounters_use, nrow = 1, common.legend = TRUE, legend = "bottom")
bot <- ggarrange(repvis_fig, repvisadm_fig, nrow = 1, common.legend = TRUE, legend = "bottom")
# quartz(type = "pdf", file = "pdfs/fig1.pdf", height = 10, w = 8)
ggarrange(top, bot, nrow = 2)
# dev.off()
# # embed the font
# embed_fonts("pdfs/fig1.pdf")
```

## Age

```{r hu_age_cat}
hu_age_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = age_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("A) Age") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 2)) +
  theme1
```

## Sex

```{r hu_sex_graph}
hu_sex_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = sex), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("B) Sex") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 2)) +
  theme1
```


## Language

```{r hu_lang_graph}
hu_lang_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = lang_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("C) Language") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 2)) +
  theme1
```

## Race

```{r hu_race_graph}
hu_race_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = race), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("D) Race") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 5)) +
  theme1
```

## Ethnicity

```{r hu_ethnicity_graph}
hu_eth_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = eth_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("E) Ethnicity") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 5)) +
  theme1
```

## Insurance
```{r hu_insurance_graph}
hu_ins_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = insurance_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("F) Insurance") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 5)) +
  theme1
```

### Supplemental Figure 1 - Demographics

```{r supfig1_demo, fig.height=10, fig.width=12}
# quartz(type = "pdf", file = "pdfs/insurance.pdf", height = 8, w = 10)
ggarrange(hu_age_fig, hu_sex_fig, hu_lang_fig, hu_race_fig, hu_eth_fig, hu_ins_fig)
# dev.off()
# # embed the font
# embed_fonts("pdfs/insurance.pdf")
```

## Arrival Method

```{r hu_arrival_graph}
hu_ar_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = meansOfArrival), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("A) Arrival Method") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```

## ED Disposition

```{r hu_eddispo_graph}
hu_eddc_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = edDispoCat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("B) ED Disposition") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```

## Hospital Discharge

```{r hu_hospdc_graph}
hu_hospdc_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = hospDispoCat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("C) Hospital Discharge Location") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```

## Acuity Level

```{r hu_acuity_graph}
hu_triage_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = factor(acuity_level_c)), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("D) Intake Triage Scores") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```

## Chief Complaint

```{r hu_cc_graph}
hu_cc_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = cc_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("E) Chief Complaint Category") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```

## ED Primary Diagnosis

```{r hu_pdx_graph}
hu_eddx_fig <- ggplot(hu_data, aes(x = vis_month)) +
  geom_bar(aes(fill = ed_dx_cat), position = position_fill()) +
  facet_grid(rows = ~housing_cat) +
  ggtitle("F) Primary ED Discharge Diagnosis") +
  xlab("") +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent()) +
  scale_fill_brewer(name = "", type = "qual", palette = "Paired", na.value = "grey") +
  guides(fill = guide_legend(nrow = 6)) +
  theme1
```


### Supplemental Figure 2 - Clinical

```{r supfig2_clin, fig.height=10, fig.width=12}
# quartz(type = "pdf", file = "pdfs/insurance.pdf", height = 8, w = 10)
## HAVE TWO CC FIGS AS A PLACEHOLDER
ggarrange(hu_ar_fig, hu_eddc_fig, hu_hospdc_fig, hu_triage_fig, hu_cc_fig, hu_eddx_fig)
# dev.off()
# # embed the font
# embed_fonts("pdfs/insurance.pdf")
```

# Raw number of visits by month, day, and time of day

```{r raw_count}
count_month_all <- data %>% group_by(vis_month, housing_screen) %>%
  summarise(n = n()) %>% mutate(housing_screen = forcats::fct_explicit_na(housing_screen))

supfig3a <- count_month_all %>%
  mutate(vis_month = factor(vis_month, levels = c("Jan", "Feb", "Mar", "Apr", "May"))) %>%
  ggplot(aes(x = vis_month)) +
  geom_point(aes(y = n, color = housing_screen)) +
  ggtitle("A)") +
  xlab("") +
  ylab("Number of Visits") +
  guides(color = guide_legend(title = "Experiencing Homelessness")) +
  theme1

# by day of the week
count_day_all <- data %>% group_by(vis_weekday, housing_screen) %>%
  summarise(n = n())

supfig3b <- count_day_all %>%
  mutate(vis_weekday = factor(vis_weekday, levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))) %>%
  ggplot(aes(x = vis_weekday)) +
  geom_point(aes(y = n, color = housing_screen)) +
  ggtitle("B)") +
  xlab("") +
  ylab("Number of Visits") +
  guides(color = guide_legend(title = "Experiencing Homelessness")) +
  theme1

# by time of day
count_time_all <- data %>% group_by(vis_hour, housing_screen) %>%
  summarise(n = n()) %>% mutate(housing_screen = forcats::fct_explicit_na(housing_screen))

supfig3c <- count_time_all %>%
  mutate(vis_hour = factor(vis_hour, levels = c(as.character(seq(0, 23))))) %>%
  ggplot(aes(x = vis_hour)) +
  geom_point(aes(y = n, color = housing_screen)) +
  ggtitle("C)") +
  xlab("") +
  ylab("Number of Visits") +
  guides(color = guide_legend(title = "Experiencing Homelessness")) +
  theme1
```

# Raw Prevelance by month, day, and time of day

```{r raw_prev}
# by month
prev_month_all <- data %>% group_by(vis_month, housing_screen) %>%
  summarise(n = n()) %>% mutate(prev = n / sum(n),
                                housing_screen = forcats::fct_explicit_na(housing_screen))

supfig3d <- prev_month_all %>%
  mutate(vis_month = factor(vis_month, levels = c("Jan", "Feb", "Mar", "Apr", "May"))) %>%
  ggplot(aes(x = vis_month)) +
  geom_point(aes(y = prev, color = housing_screen)) +
  ggtitle("D)") +
  xlab("") +
  scale_y_continuous(name = "Percentage of Visits", labels = scales::label_percent(), limits = c(0, 1)) +
  guides(color = guide_legend(title = "Experiencing Homelessness")) +
  theme1

# by day of the week
prev_day_all <- data %>% group_by(vis_weekday, housing_screen) %>%
  summarise(n = n()) %>% mutate(prev = n / sum(n))

supfig3e <- prev_day_all %>%
  mutate(vis_weekday = factor(vis_weekday, levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))) %>%
  ggplot(aes(x = vis_weekday)) +
  geom_point(aes(y = prev, color = housing_screen)) +
  ggtitle("E)") +
  xlab("") +
  scale_y_continuous(name = "Percentage of Visits", labels = scales::label_percent(), limits = c(0, 1)) +
  guides(color = guide_legend(title = "Experiencing Homelessness")) +
  theme1

# by time of day
prev_time_all <- data %>% group_by(vis_hour, housing_screen) %>%
  summarise(n = n()) %>% mutate(prev = n / sum(n),
                                housing_screen = forcats::fct_explicit_na(housing_screen))
supfig3f <- prev_time_all %>%
  mutate(vis_hour = factor(vis_hour, levels = c(as.character(seq(0, 23))))) %>%
  ggplot(aes(x = vis_hour)) +
  geom_point(aes(y = prev, color = housing_screen)) +
  ggtitle("F)") +
  xlab("") +
  scale_y_continuous(name = "Percentage of Visits", labels = scales::label_percent(), limits = c(0, 1)) +
  guides(color = guide_legend(title = "Experiencing Homelessness")) +
  theme1
```

# Supplemental Figure 3 - Raw Percentage and Absolute Counts

```{r supfig3, fig.height=10, fig.width=12}
ggarrange(supfig3a, supfig3b, supfig3c, 
          supfig3d, supfig3e, supfig3f,
          nrow = 2, ncol = 3,
          common.legend = TRUE, legend = "bottom")
```

# Boostrap to get estimates of prevalence by month, day, and time of day

```{r boot_prev, warning=FALSE, eval = FALSE}
#### FIX WITH CATEGORIES ###

# start by setting a seed
set.seed(seed = 1111)

# get baseline values
prev_tot <- sum(data$housing_screen == "Yes", na.rm = TRUE) / nrow(data)
prev_month <- data %>% group_by(vis_month, housing_screen) %>%
  summarise(n = n()) %>% mutate(prev = n / sum(n)) %>%
  filter(housing_screen == "Yes")
prev_day <- data %>% group_by(vis_weekday, housing_screen) %>%
  summarise(n = n()) %>% mutate(prev = n / sum(n)) %>%
    filter(housing_screen == "Yes")
prev_time <- data %>% group_by(vis_hour, housing_screen) %>%
  summarise(n = n()) %>% mutate(prev = n / sum(n)) %>%
    filter(housing_screen == "Yes")
prev_daytime <- data %>% group_by(vis_weekday, vis_hour, housing_screen) %>%
  summarise(n = n()) %>% mutate(prev = n / sum(n)) %>%
    filter(housing_screen == "Yes")

# make a dataframe with prevalence
prev_df <- tibble(type = c("Overall", as.character(prev_month$vis_month), as.character(prev_day$vis_weekday), 
                           as.character(prev_time$vis_hour), as.character(prev_daytime$vis_weekday)),
                  time = c(rep("99", 37), as.character(prev_daytime$vis_hour)),
                  Est = c(prev_tot, prev_month$prev, prev_day$prev, prev_time$prev, prev_daytime$prev),
                  LB = NA,
                  UB = NA,
                  CI = NA)

# make a function
boot_prev <- function(data) {
  # generate bootstrapped sample
  resamp <- sample_n(data, size = nrow(data), replace = TRUE)
  # pull out prevelances
  prev_tot <- sum(resamp$housing_screen == "Yes", na.rm = TRUE) / nrow(resamp)
  prev_month <- resamp %>% group_by(vis_month, housing_screen) %>% 
    summarise(n = n()) %>% mutate(prev = n / sum(n)) %>%
    filter(housing_screen == "Yes")
  prev_day <- resamp %>% group_by(vis_weekday, housing_screen) %>%
    summarise(n = n()) %>% mutate(prev = n / sum(n)) %>%
    filter(housing_screen == "Yes")
  prev_time <- resamp %>% group_by(vis_hour, housing_screen) %>%
    summarise(n = n()) %>% mutate(prev = n / sum(n)) %>%
    filter(housing_screen == "Yes")
  prev_daytime <- resamp %>% group_by(vis_weekday, vis_hour, housing_screen) %>%
    summarise(n = n()) %>% mutate(prev = n / sum(n)) %>%
      filter(housing_screen == "Yes")
  
  # make final df
  tibble(type = c("Overall", as.character(prev_month$vis_month), as.character(prev_day$vis_weekday), 
                           as.character(prev_time$vis_hour), as.character(prev_daytime$vis_weekday)),
                  time = c(rep("99", 37), as.character(prev_daytime$vis_hour)),
                  boot_prev = c(prev_tot, prev_month$prev, prev_day$prev, prev_time$prev, prev_daytime$prev))
}

# initiate output
out <- prev_df
for(i in 1:1000) {
  out <- left_join(out, boot_prev(data), by = c("type", "time"), suffix = c("", i))
}

# calculate LB and UB
LBs <- out %>%
  select(boot_prev:boot_prev1000) %>%
  t() %>% as_tibble() %>%
  map_dbl(~quantile(.x, 0.025, na.rm = TRUE))

UBs <- out %>%
  select(boot_prev:boot_prev1000) %>%
  t() %>% as_tibble() %>%
  map_dbl(~quantile(.x, 0.975, na.rm = TRUE))

out <- out %>%
  mutate(LB = LBs,
         UB = UBs,
         CI = paste0("(", round(LB, 3), ", ", round(UB, 3), ")"))
out
# will want to save this output so can only run this once
fin_boot <- out %>% select(type:CI)

# output bootstrapped values
Save(fin_boot)
```

```{r boot_pull}
Load(fin_boot)
```

## Prevalence by Month
```{r month_prev}
month_fig <- fin_boot %>%
  filter(type %in% c("Jan", "Feb", "Mar", "Apr", "May")) %>%
  mutate(type = factor(type, levels = c("Jan", "Feb", "Mar", "Apr", "May"))) %>%
  ggplot(aes(x = type)) +
  geom_errorbar(aes(ymin = LB, ymax = UB), width = 0.1) +
  geom_point(aes(y = Est)) +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent(), limits = c(0, 0.125)) +
  xlab("") +
  ggtitle("A) Percentage by Month") +
  theme1 +
  theme(axis.text.x = element_text(angle = 0))
```

## Prevalence by Day
```{r day_prev}
day_fig <- fin_boot %>%
  filter(type %in% c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun") & time == "99") %>%
  mutate(type = factor(type, levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))) %>%
  ggplot(aes(x = type)) +
  geom_errorbar(aes(ymin = LB, ymax = UB), width = 0.1) +
  geom_point(aes(y = Est)) +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent(), limits = c(0, 0.125)) +
  xlab("") +
  ggtitle("B) Percentage by Weekday") +
  theme1 +
  theme(axis.text.x = element_text(angle = 0))
```

## Prevalence by Time of Day
```{r time_prev}
time_fig <- fin_boot %>%
  filter(type %in% as.character(seq(0, 23)) & time == "99") %>%
  mutate(type = factor(type, levels = c(as.character(seq(0, 23))))) %>%
  ggplot(aes(x = type)) +
  geom_errorbar(aes(ymin = LB, ymax = UB), width = 0.1) +
  geom_point(aes(y = Est)) +
  ylim(0, 0.125) +
  scale_y_continuous(name = "Percentage", labels = scales::label_percent(), limits = c(0, 0.125)) +
  xlab("Hour") +
  ggtitle("C) Percentage by Hour") +
  theme1 +
  theme(axis.text.x = element_text(angle = 0))
```

## Prevalence by Day and Time
```{r all_prev}
daytime_fig <- fin_boot %>%
  filter(time != "99") %>%
  mutate(type = factor(type, levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")),
         time = factor(time, levels = c(as.character(seq(0, 23))))) %>%
  ggplot(aes(x = type)) +
  geom_tile(aes(y = time, fill = Est)) +
  geom_text(aes(y = time, label = paste0(percent(Est, accuracy = 0.1), "\n", 
                                         "(", percent(LB, accuracy = 0.1),
                                         ", ", percent(UB, accuracy = 0.1), ")")), 
            size = 2.75, color = "white") +
  scale_fill_gradient(name = "Percentage", high = "#132B43", low = "#56B1F7") +
  ylab("Hour") +
  xlab("Day") +
  ggtitle("D) Percentage by Weekday and Time") +
  theme1 +
  theme(axis.text.x = element_text(angle = 0))
```

## Figure 4 - Prevalence Figure

```{r fig4, fig.height=10, fig.width=12}
# quartz(type = "pdf", file = "pdfs/fig2.pdf", height = 10, w = 12)
left_fig <- ggarrange(month_fig, day_fig, time_fig, nrow = 3)
ggarrange(left_fig, daytime_fig, common.legend = TRUE, legend = "bottom")
# dev.off()
# # embed the font
# embed_fonts("pdfs/fig2.pdf")
```

# Weather Data

```{r pull_weather, eval =FALSE}
# https://docs.ropensci.org/rnoaa/
# my web token: Email:	daniel.e.sack@gmail.com
# Token:	dGFZnaNPcYqMsRIhDhEMxzSCgvmWmZqr

# pull nashville data (Jan 5 to May 16, 2023)

# variable options
# https://www1.ncdc.noaa.gov/pub/data/ghcn/daily/readme.txt

# temperature data
# https://www.ncdc.noaa.gov/cdo-web/datatools/findstation
# max temp (TMAX - in tenths of degrees celcius)
# min temp (TMIN - in tenths of degrees celcius)
# average temp (TAVG in tenths of degrees celcius)
# ADPT (average dew point temperature in tenths of degrees celcius)
# RHAV = Average relative humidity for the day (percent)

# Precipitation
# PRCP (tenths of mm)
# SNOW (snowfall in mm)

# Wind
# WSFG = Peak gust wind speed (tenths of meters per second)

# vector of datatypes"WSFG"
datatypes <- c("TMAX", "TMIN", "TAVG", "ADPT", "RHAV", "PRCP", "SNOW", "WSFG", "WT11")

# What is available at the Nashville Station (CITY:US470016)
# ncdc_locs(locationcategoryid='CITY', sortfield='name', sortorder='desc', limit = 1000)$data

# Shelby Bottoms: GHCND:USC00408238
# BNA: GHCND:USW00013897
# BNA Berry Field: GHCND:USC00406403
# Oak Hill: GHCND:US1TNDV0163
# Belle Meade: GHCND:US1TNDV0157
# Spring Hill South: GHCND:US1TNDV0117

# for bna (b/c most complete) - has air temp (celcius tenths), precipitation (rain tenth of mm, snow in mm), and weather type 11 (high or damaging winds)
wet_data_bna <- ncdc(datasetid = "GHCND", stationid = "GHCND:USW00013897", datatypeid = datatypes, startdate = "2023-01-05",
             enddate = "2023-05-16", limit = 1000)$data %>% select(date:value) %>% pivot_wider(names_from = "datatype", values_from = "value") %>%
  mutate(rain = PRCP / 100, # in cm
         snow = SNOW / 10, # in cm
         avg_temp = TAVG / 10, # in celcius
         max_temp = TMAX / 10, # in celcius
         min_temp = TMIN / 10) # in celcius
Save(wet_data_bna)
```

```{r plot_weather}
# graph values over time
Load(wet_data_bna)
# rain and snow
ggplot(wet_data_bna) +
  geom_point(aes(x = date, y = rain), color = "blue") +
  geom_point(aes(x = date, y = snow), color = "grey50")

# temp
ggplot(wet_data_bna) +
  geom_point(aes(x = date, y = min_temp), color = "gold") +
  geom_point(aes(x = date, y = avg_temp), color = "orange") +
  geom_point(aes(x = date, y = max_temp), color = "red")
```

# Weather by prevalence

```{r temp_prev}
# plot average temperature by prevalence

# first calculate daily prevalence
prev_date <- data %>% group_by(vis_date, housing_screen) %>%
  summarise(n = n()) %>% mutate(prev = n / sum(n)) %>%
    filter(housing_screen == "Yes")

# combine with weather data
weather <- left_join(wet_data_bna %>% mutate(vis_date = as_date(date)), prev_date %>% mutate(vis_date = as_date(vis_date)), by = "vis_date")
```

## Precipitation

```{r precip_plot}
rainfig <- ggplot(weather, aes(x = rain, y = prev)) +
  geom_point() +
  geom_smooth(method = "loess") +
  ggtitle("A) Precipitation") +
  ylab("Proportion") +
  xlab("Rain (cm)") +
  theme1 +
  theme(axis.text.x = element_text(angle = 0))
```

## Minimum Temp

```{r mint_plot}
mintfig <- ggplot(weather, aes(x = min_temp, y = prev)) +
  geom_point() +
  geom_smooth(method = "loess") +
  ggtitle("B) Minimum Temperature") +
  ylab("Proportion") +
  xlab("Temperature (Celcius)") +
  theme1 +
  theme(axis.text.x = element_text(angle = 0))
```

```{r avgt_plot, eval = FALSE}
## Average Temp
ggplot(weather, aes(x = avg_temp, y = prev)) +
  geom_point() +
  geom_smooth(method = "loess")
```

## Maximum Temp

```{r maxt_plot}
maxtfig <- ggplot(weather, aes(x = max_temp, y = prev)) +
  geom_point() +
  geom_smooth(method = "loess") +
  ggtitle("C) Maximum Temperature") +
  ylab("Proportion") +
  xlab("Temperature (Celcius)") +
  theme1 +
  theme(axis.text.x = element_text(angle = 0))
```

### Supplemental Figure 4 - Weather

```{r supfig4, fig.height=5, fig.width=12}
ggarrange(rainfig, mintfig, maxtfig, nrow = 1)
```